Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-08 paper/paper.tex
paragraph about the other subgraph isomorphism portfolio paper

>>>>

\medskip

Battiti and Mascia~\cite{battiti_algorithm_2007} were the first to propose
algorithm portfolios for subgraph isomorphism problems. However, they only
consider a pure parallel portfolio without a selection mechanism consisting of
only two solvers. In addition, our instance set is much larger and considers
both hard and unsatisfiable instances.
